Grove: A Convergent Collaborative Structure-Editor Calculus

### 2021-02-16 grove-paper.tex
drop spurious figure
elaborate on the meaning of v = min(ancestors(v))

The fourth component $W$ is the set of expressions derived from the remaining vertices, which must necessarily form cyclic structures we call wreaths, where each vertex has exactly one parent.

In $W$, $\ancestors(v)$ is the set of vertices for which there is a path to $v$.
Note that $v = \min(\ancestors(v))$ only if $v$ is part of a cycle.

@@

\begin{figure}[b]
\begin{align*}
  \parents(v) &= \{v' : \exists \e = (u, v', p, v), G(\e) = \Plus\} \\
  \ancestors(v) &= \parents(v) \cup \ancestors(\parents(v))
  \children(v, p) = \{v' : \exists \e (u, v, p, v'), G(\e) = \Plus\}
\end{align*}

>>>>

The fourth component $W$ is the set of expressions derived from the remaining vertices, which form cyclic structures we call wreaths, where each vertex has exactly one parent.
In $W$, $\ancestors(v)$ is the set of vertices for which there is a path to $v$.
Note that $v = \min(\ancestors(v))$, where $\min(\{v_{\id{u_1}}, \ldots, v_{\id{u_n}}\}) = v_{\id{u_k}}$ such that $u_k = \min(\{u_{\id{1}}, \ldots, u_{\id{n}}\})$, holds only if $v$ is part of a cycle.

@@
